\gettitle

### 2020-01-26 assignment6/submission6.tex
done 6.3.c

	\draw[->, thick] (4.5, 3) -- node[pos=0.6, sloped, above] {$ < m_2||m_4> $} (11, 6);
	\draw[->, thick] (4.5, 3) -- node[pos=0.7, sloped, below] {$ < m_2||m_4> $} (7, 0);
	\end{tikzpicture}
	\caption{Execution of Algorithm 1}
	\label{fig:3b}
\end{figure}
\subsubsection*{ii.} Otherwise the total ordering can be violated, and therefore the correctness.
\subsubsection*{iii.}

>>>>

	\draw[->, thick] (4.5, 3) -- node[pos=0.6, sloped, above] {$ < m_2||m_4> $} (11, 6);
	\draw[->, thick] (4.5, 3) -- node[pos=0.7, sloped, below] {$ < m_2||m_4> $} (7, 0);
	\end{tikzpicture}
	\caption{Execution of Algorithm 1}
	\label{fig:3b}
\end{figure}
\subsubsection*{ii.} As seen in figure \ref{fig:3b} the fifo ordering can be violated, and therefore the correctness.
\subsubsection*{iii.} Append the last sent message as causal dependency to the new message. The reciever can then guarantee fifo ordering again.
